### 2012-12-04 inst/examples/policycosts/figure4.Rmd
fixed figure4 -- extract policycost separately from bigloop

``` {r}
profit <- profit_harvest(price = 10, c0 = 30, c1 = 0)
c2 <- seq(0, 20, length.out = 40)
```

@@

``` {r  quadcosts, dependson="bigloop"}
quad <- 
  sfLapply(c2, function(c2){
  effort_penalty = function(x,h) c2 * h / x
  policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                        profit, delta, reward, penalty = none, 
                        effort_penalty)
})
dat <- cbind(policies, quad)
````

>>>>

``` {r}
profit <- profit_harvest(price = 10, c0 = 30, c1 = 0)
c2 <- exp(seq(0, log(21), length.out = 20))-1
```

@@

``` {r  quadcosts, dependson="bigloop"}
quad <- 
  sfLapply(c2, function(c2){
  effort_penalty = function(x,h) c2 * h / x
  policycost <- optim_policy(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                        profit, delta, reward, penalty = none, 
                        effort_penalty)
})
policies <- c(policies, quad=list(quad))
````

Extract the policy cost

```{r}
i <- which(x_grid > K)[1]
dat <- 
lapply(policies, function(penalty) 
  sapply(penalty, function(c2_run)
    max(c2_run$penalty_free_V[i,]) 
  )
)
```
